---
title: "Evaluating vaccination policy proposal: Vaccinate only seronegative"
subtitle: Based on epidemic model fit to LAC data as of `r Sys.Date()`
author: "Abigail Horn"
output:
  html_document:
    css: styles.css
    toc: yes
    toc_depth: 2
    toc_float: yes
editor_options:
  chunk_output_type: console
---

```{r, include=FALSE, eval=FALSE}
# NOTES TO REMEMBER
# Both Susceptible and Recovered are vaccinated
# Vaccine efficacy delay vx.delay stored in prior_param.R (takes hold immediately after vx.delay)
```



<!--Initialize-->

``` {r setup, include=FALSE}

### Install necessary packages and get started

library(reshape2)
library(tidyverse)
library(ggplot2)
library(plotly)
library(ggrepel)
library(bindata)
library(odin)
library(fitR)
library(knitr)
library(EasyABC)
library(gridExtra)
library(odin)
library(lubridate)
library(EasyABC)
library(gridExtra)
library(kableExtra)
library(plyr)
library(dplyr)
library(data.table)
library(scales)
library(EasyABC)
library(patchwork)

library(tidyr)
library(readr)
library(purrr)
library(tibble)
library(stringr)
library(forcats)
library(network)
library(tidygraph)
library(ggraph)
library(visNetwork)
library(networkD3)
library(ggmosaic)
library(formattable)
library(DT)
library(reshape)
library(here)
library(fs)
library(MASS)
library(plotly)


lang_output <- function(x, lang) {
  cat(c(sprintf("```%s", lang), x, "```"), sep = "\n")
}
r_output <- function(x) lang_output(x, "r")

knitr::opts_chunk$set(
  fig.width = 9.5,
  fig.height = 8,
  eval=TRUE,
  echo=FALSE,
  warning=FALSE,
  cache=FALSE,
  message=FALSE,
  include=TRUE
  )

code.dir=here("code/")
data.dir=here("data/")
result.dir = here("results/")
fig.dir = here("figs/")
output.dir = here("output/")
code.paper.dir=here("code/epi_model_code")
code.risk.dir=here("code/risk_model_code/")
code.scenarios.dir=here("code/scenarios_code/")
```

<!--Set global options-->

```{r options, include=FALSE}
print.output <- FALSE
days.truncate <- 0
endDatePlotGlobal <- as.Date("2021-01-31")
last.date.plot.Vx <- as.Date("2021-01-20") + 100
```


<!--Read in epidemic model, functions, COVID data-->

```{r read-in-model-supporting-functions, include=FALSE}

###################################################################################################
## LOAD EPIDEMIC MODELS
## And compile the model
path_seihqdr_model <- path(code.paper.dir, "stochastic_SEIAHQDR_Alphat_rt.R")
seihqdr_generator <- odin::odin(path_seihqdr_model)

path_Vx_model <- path(code.paper.dir, "stochastic_SEIAHQDR_Vx_sero.R")
Vx_generator <- odin::odin(path_Vx_model)


###################################################################################################
## LOAD DATA PROCESSING AND MODEL ESTIMATING FUNCTIONS
model_functions <- path(code.paper.dir, "data_model_fun.R")
source(model_functions)

###################################################################################################
## LOAD PLOTTING FUNCTIONS
plot_code <- path(code.paper.dir, "plotting_fun_NEW.R")
source(plot_code)

###################################################################################################
## LOAD TABLES FUNCTIONS
tables_code <- path(code.paper.dir, "tables_fun.R")
source(tables_code)

###################################################################################################
## COVID INPUT DATA
# latest_data: cumulative and daily counts for "Htotcum","D","Vcum","Idetectcum","H_new","D_new"
# no_obs: number of observation days
latest_data <- latest_covid_data(truncate=days.truncate)
no_obs <- nrow(latest_data)

```


<!--Model Fitting-->

```{r include=FALSE}

## SOURCE PRIOR PARAMETERS
## Provides output in form of a prior.par list
## Note: Beta(t), Alpha(t), Kappa(t), Delta(t) are read in from file
prior_param_input <- path(code.paper.dir, "prior_param.R")
source(prior_param_input)
# prior.par

## SUMMARY STATISTICS COMPUTED ON DATA
summarydata <- sum.stats.SIMTEST(latest_data,include.R = FALSE)
model.R <- model.1sim.stats.no.R  # From supporting_functions

### NUMBER OF OUTPUTS
# n_calibration = 10000
# n_rec = 2000

n_calibration = 1000
n_rec = 100

## FIT MODEL
ABC_out<-ABC_mcmc(method="Marjoram",model=model.R,prior=prior.par,
                       summary_stat_target=summarydata, n_calibration=n_calibration,
                       tolerance_quantile=0.1,verbose=FALSE,progress=TRUE, n_rec=n_rec)

ABC.par.out <- as.data.frame(ABC_out$param)
ABC.out.mat <- ABC_out$param
par.vec.length <- nrow(ABC_out$param)

```


<!--Simulate model-->
<!--Get compartment variables over time with CI-->
<!--Get CFR/IFR-->

```{r include=FALSE}
###################################################################################################
## GET VACCINE EFFICACY DELAY "vx.delay" from prior_param_input
prior_param_input <- path(code.paper.dir, "prior_param.R")
source(prior_param_input)

ABC.out.mat <- ABC_out$param
par.vec.length <- nrow(ABC_out$param)
iter <- 10
time.steps <- last.date.plot.Vx - as.Date("2020-03-01") + 50
vars.to.plot <- vars.plus.Vx
vx.delay <- 20
vx.coverage <- .25

## FUNCTION MODEL.OUTPUT.TO.PLOT.SIM
## Calculates mean and CI of each estimated parameter & CFR/IFR
## Uses correlated.param.SIM
## Reads in Beta, Alpha, Kappa, Delta from file
traj.0 <- model.output.to.plot.SIM(ABC.out.mat=ABC.out.mat, vx.delay=vx.delay, vx.coverage = vx.coverage, par.vec.length=par.vec.length, iter=iter, time.steps=time.steps, vars.to.plot = vars.to.plot)

```


```{r include=FALSE}

###################################################################################################
## Plot all variables current date

time.steps.4.plot = last.date.plot.Vx - as.Date("2020-03-01") +1
data.in <- latest_data
vars.to.plot <- vars.plus.Vx

plot.all.variables.curr.date <- 
plot.model.data.all(traj.CI = traj.0, data.in = data.in, init.date.data = "2020-03-01", date.offset.4plot = 0,  time.steps.4plot=time.steps.4.plot,
                    vars.to.plot=vars.plus.Vx)

if (print.output==TRUE){
  pdf(file = path(output.dir, "plot.all.variables.pdf"), width=10, height =10)
  plot.all.variables.curr.date
  dev.off()
}
#plot.all.variables.curr.date

```

# Model calibration

## Model fits {.tabset}

Summarizes the epidemic model fit with COVID-19 data for LAC from March 1 through `r as.Date("2020-03-01") + no_obs` for all disease states across multiple views: New cases, representing new daily incidence; the current number in a compartment at a specific date, relevant for understanding current prevalence rates and comparing with healthcare capacity limitations; and cumulative counts until a specific date. Observed data for available compartments with cases attributable to nursing home residents removed, are plotted as black dots. The figure demonstrates that good model fits are achieved in all compartments across time.

* **New = new daily incidence**
* **Current = current census in compartment** 
* **Cumulative = running total over time**
* Black dots depict COVID-19 data, with counts from outbreaks in nursing homes removed
* The dashed line represents healthcare resource capacity limits

```{r include=FALSE}

###################################################################################################
## Plot all variables current date

time.steps.4.plot = as.numeric(endDatePlotGlobal - as.Date("2020-03-01") + 2)
data.in <- latest_data
vars.to.plot <- vars.plus.Vx

plot.all.variables.curr.date <- 
plot.model.data.all(traj.CI = traj.0, data.in = data.in, init.date.data = "2020-03-01", date.offset.4plot = 0, time.steps.4plot=time.steps.4.plot,
                    vars.to.plot=vars.plus.Vx)

if (print.output==TRUE){
  pdf(file = path(output.dir, "plot.all.variables.pdf"), width=10, height =10)
  plot.all.variables.curr.date
  dev.off()
}
#plot.all.variables.curr.date

```

```{r include=FALSE}

###################################################################################################
## Plot all variables plus 15 days

time.steps.4.plot = as.numeric(as.Date(last.date.plot.Vx) - as.Date("2020-03-01") + 15)
data.in <- latest_data
vars.to.plot <- vars.plus.Vx

plot.all.variables.vx.timeline <- 
plot.model.data.all(traj.CI = traj.0, data.in = data.in, init.date.data = "2020-03-01", date.offset.4plot = 0, time.steps.4plot=time.steps.4.plot,
                    vars.to.plot=vars.plus.Vx)

if (print.output==TRUE){
  pdf(file = path(output.dir, "plot.all.variables.pdf"), width=10, height =10)
  plot.all.variables.vx.timeline
  dev.off()
}
#plot.all.variables.plus.15.days
```

### Model fits through `r Sys.Date()`

```{r}
plot.all.variables.curr.date
```

### Model **projections**

Projections **under the assumption of the infectious rate as of `r Sys.Date()`** 

```{r}
plot.all.variables.vx.timeline
```








# Vaccination Scenarios 

**Evaluation of proposed policy: Vaccinate only those that are sero negative (susceptible)**

<!---
Get Alpha Kappa Delta table
--->

```{r include=FALSE}
###################################################################################################
## GET MODEL OUTPUT: summary

startDatePlot <- as.Date("2020-03-01")
endDatePlot <- endDatePlotGlobal
all_day_1s <- seq(startDatePlot,endDatePlot,by='month')
all_day_15s <- all_day_1s+14
date.in <- sort(c(all_day_1s,all_day_15s))
tables.out <- summary.table.param.CFR.IFR(traj.CI=traj.0, ABC_out=ABC_out, date.in=date.in, use.mean.select = 1, round.by.in=4)

```

<!--- 
Read in data
--->

```{r include=FALSE}
###############################################################################################################
## Read in marginal risk probability P(H|I), P(Q|H), P(D|Q) for each risk profile q, calculated by the JAM model
## Data coming from: Guan et al. 2020, Petrilli et al. 2020
Pr.H <- read.csv(path(data.dir, "Pr.H.csv"), sep=",", header=TRUE,row.names = 1)
Pr.Q <- read.csv(path(data.dir, "Pr.Q.csv"), sep=",", header=TRUE,row.names = 1)
Pr.D <- read.csv(path(data.dir, "Pr.D.csv"), sep=",", header=TRUE,row.names = 1)

## Get profile matrix X.mat
X.mat <- as.matrix(dplyr::select(Pr.H, -1))
n_factors <- ncol(X.mat)
n_profiles <- nrow(X.mat)

#########################################################################################################
## Read in prevalence of each risk factor p in the population for LA County
## Data coming from:
#### [Los Angeles County Health Survey](http://www.publichealth.lacounty.gov/ha/hasurveyintro.htm)
#### [California Health Information Survey](http://ask.chis.ucla.edu)
Pop.prevalence <- read.csv(path(data.dir, "Pop.prevalence.LA.csv"), sep=",", header=TRUE,row.names = 1 )
Pop.prev.matrix<-as.matrix(Pop.prevalence)

#########################################################################################################
## Read in correlation structure, $\Sigma$, between the risk factors p
## Correlation structure is weighted according to the prevalence of each race/ethnicity in LA County
## Calculated using data coming from: The National Health and Nutrition Examination Survey (NHANES)
SIGMA <- read.csv(path(data.dir, "SIGMA.csv"), sep=",", header=TRUE,row.names = 1)

```

<!---
Calculate prevalence of each profile in overall LAC population
--->

```{r riskprofiles, include=FALSE, eval=TRUE}
calc_profile_prev<- path(code.risk.dir, "calc_profile_prev.R")
source(calc_profile_prev)

## OUTPUT
# profile.cnt.freq
```

<!---
Estimate risk probabilities with baseline from epidemic model
--->

```{r estimate-risk-integrated}

##################################################
## INPUTS: TIMES
### Chosen times to run analysis at

t1 <- "2020-05-15"
t2 <- "2020-12-15"
table.dates <- c("May.15", "Jan.15")
times <- c("t1","t2")
times.dates <- as.Date(c(t1,t2))
n.times <- length(times)

# t2 <- "2020-07-15"
# t3 <- "2020-09-15"
# t4 <- "2020-10-15"
# table.dates <- c("May.15","Jul.15","Sep.15","Oct.15")
# times.dates <- as.Date(c(t1,t2,t3,t4))
# times <- c("t1","t2","t3","t4")


##################################################
## INPUTS: OBSERVED LAC DATA ON ILLNESSES
### Observed LAC age prevalence in (I) infections
n.dates.LAC.obs.age <- length(times)
freq.LAC.obs.age <- matrix(nrow=3, ncol=n.dates.LAC.obs.age)
colnames(freq.LAC.obs.age) <- times
rownames(freq.LAC.obs.age) <- c("Age0.19","Age20.64","Age65.")

freq.LAC.obs.age[,1] <- c(0.035, 0.749, 0.216)  # May.15
freq.LAC.obs.age[,2] <- c(0.15, 0.728, 0.122)  # Jan.15


##################################################
## INPUTS: EPIDEMIC MODEL
## Get mean estimates of Alpha(t), Kappa(t), Delta(t) at each time point 
akd_table <- tables.out[[2]]
table1 <- akd_table
for (i in 1:2){  table1[i,] <- akd_table[i,] %>% mutate_if(is.character, function(x) unlist(strsplit(x, " "))[1])}
table1 <- as.data.frame(apply(table1, 2, as.numeric)) 
rownames(table1) <- c("t1","t2")

## Create extra rows representing Alpha, Kappa, Delta values for t > 2 (with same values for Alpha, Kappa, Delta as t2)
if (n.times > 2){ 
  for (exrow in 3:n.times) table1[exrow,] <- table1[2,] 
  rownames(table1) <- times
  }

risk.probs.POSTERIORS <- table1

##################################################
## INPUTS: PROFILE FREQUENCY
### Estimated frequency of each risk profile
freq.PREV.q <- as.vector(profile.cnt.freq[,1])

##################################################
## INPUTS: JAM ESTIMATED CONDITIONAL RISK EFFECTS
### Read in JAM produced conditional effect estimates
psi.mat = read.csv(path(data.dir, "psi.conditional.effect.estimates.csv"), sep=",", header=TRUE,row.names = 1)
rownames(psi.mat) <- colnames(X.mat)
psi.mat[1,] <- c(rep(-1,times=3))
psi.mat[4,] <- c(rep(2,times=3))

##################################################
## APPLY CODE TO GET ESTIMATE RISK PROBABILITIES WITH BASELINE FROM EPIDEMIC MODEL
calc_integrated_risk_model<- path(code.risk.dir, "integrated_risk_model.R")
source(calc_integrated_risk_model)

# Pr.freq.FUN.out <- Pr.freq.FUN(X.mat=X.mat, freq.PREV.q = freq.PREV.q, 
#                                freq.LAC.obs.age=freq.LAC.obs.age, logit.SEIR.est=logit.SEIR.est,psi.mat=psi.mat)
# ### OUTPUTS
# Pr.OUT <- Pr.freq.FUN.out[[1]]
# freq.OUT <- Pr.freq.FUN.out[[2]]   

```



# Vaccination Scenarios

Parameters modeled in scenarios:

$R(t)$ scenarios (starting from 1-20-20 on):

- $R(t) = 1.9$ -- value estimated as of `r Sys.Date()` 
- $R(t) = 1.5$ -- a hypothetical reduced value
- $R(t) = 2.5$ -- a hypothetical increased value

- Vaccination starting date: 12-15-20 (from LA Times)
- Vaccination rate 12-15-20 to 1-20-21: 8500 vaccines given per day (from LA Times)
- Vaccination rate 1-20-21 -- on: 0, 10k, 20k, 30k, 40k, 50k vaccines given per day 
- Date 65+ group starts vaccination: 2-1-21 (as promised)
- Vaccine coverage rate in 65+ (% final updake by population): 88% (from Understanding America Study)
- **Sero+ vaccination scenarios considered: 0%, 50%, 100% of recovered (sero+) individuals are (unnecessarily) vaccinated**

<!---
Scenarios: Sero+ included
--->

```{r scenarios-REALISTIC, include=FALSE}

##################################################
## SOURCE SCENARIOS FUNCTIONS
path_Vx_model <- path(code.paper.dir, "stochastic_SEIAHQDR_Vx_sero.R")
Vx_generator <- odin::odin(path_Vx_model)

#scenarios_functions <- path(code.scenarios.dir, "scenarios_fun_TEST.R")
scenarios_functions <- path(code.scenarios.dir, "scenarios_fun_sero_DIFF.R")
source(scenarios_functions)

heatmap_functions <- path(code.scenarios.dir, "heatmap_functions.R")
source(heatmap_functions)

##################################################
## INPUTS for getting % removed for various scenarios

start_time = 45
num.to.run = 20
ABC.out.mat.scenarios = ABC.out.mat[c(1:num.to.run),]
iter=5
time.steps <- last.date.plot.Vx - as.Date("2020-03-01") + 5
vx.delay <- 20
fn_t_readin_input = "fn_t_readin.csv"

##################################################
## Vacination overall scenarios ALL

n.vx.scenario <- 6
vx.scenarios.mat <- matrix(NA, nrow=n.vx.scenario, ncol=5)
colnames(vx.scenarios.mat) <- c("index","name.vx", "vx_y.vals","vx.coverage","delay.start.65.vx")
vx.scenarios.mat[,"index"] <- c(1:n.vx.scenario)
vx.scenarios.mat[,"name.vx"] <- c("0", "10k", "20k", "30k", "40k","50k")
vx.scenarios.mat[,"vx_y.vals"] <- c("nvx_y", "nvx_10k", "nvx_20k", "nvx_30k", "nvx_40k","nvx_50k")
vx.scenarios.mat[,"vx.coverage"] <- rep(.88, n.vx.scenario)  
vx.scenarios.mat[,"delay.start.65.vx"] <- rep(36, n.vx.scenario) 

#vx.scenarios.mat <- vx.scenarios.mat[c(1:2),]

mu.scenario.in <-  c(.55,.42, .71) #seq(0.1,.9,by=.1) #seq(0.1,.6,by=.25)
sero.scenario.in <- c(1, 0.5, 0.01)

## Run the scenarios
scenarios.out.realistic.ALL.diff <- correlated.param.SCENARIOS.diff(fn_t_readin_input=fn_t_readin_input, ABC.out.mat=ABC.out.mat.scenarios, iter=iter, time.steps=time.steps, 
                                                             vx.scenarios.mat=vx.scenarios.mat, 
                                                             sero.scenario.in=sero.scenario.in,
                                                             mu.scenario.in=mu.scenario.in, 
                                                             X.mat=X.mat, freq.PREV.q=freq.PREV.q, freq.LAC.obs.age=freq.LAC.obs.age,
                                                             logit.SEIR.est=logit.SEIR.est, psi.mat=psi.mat, vx.delay=vx.delay)

traj.CI <- scenarios.out.realistic.ALL.diff[[1]]
traj.CI.diff <- scenarios.out.realistic.ALL.diff[[2]]

```





<!---
Heatmaps
--->


```{r}

var.to.plot <- "D"
#y.var <- "R0.id"
y.var <- "sero.id"
x.var <- "vx.id"
scale.x.labels=NULL
scale.y.labels <- c(0, 0.5, 1)
rep.0 = NULL
plot.0 = TRUE

plot.title <- "Total Deaths: Vax Rate vs. % Sero Negative Vax Comparison"
filter.coverage <- 0
filter.65.delay <- 0

plot.title <- "R(t) = 1.9"
data <- traj.CI %>% filter(R0.id==1.9)
R0vsRate.D.1.9 <- plot_heatmap(data=data,x.var=x.var,y.var=y.var, var.to.plot = var.to.plot, filter.coverage = filter.coverage, filter.65.delay = filter.65.delay, plot.title = plot.title, scale.x.labels=scale.x.labels,scale.y.labels=scale.y.labels,rep.0=rep.0,plot.0=plot.0)
#R0vsRate.D.1.9

plot.title <- "R(t) = 1.5"
data <- traj.CI %>% filter(R0.id==1.5)
R0vsRate.D.1.5 <- plot_heatmap(data=data,x.var=x.var,y.var=y.var, var.to.plot = var.to.plot, filter.coverage = filter.coverage, filter.65.delay = filter.65.delay, plot.title = plot.title, scale.x.labels=scale.x.labels,scale.y.labels=scale.y.labels,rep.0=rep.0,plot.0=plot.0)
#R0vsRate.D.1.5

plot.title <- "R(t) = 2.5"
data <- traj.CI %>% filter(R0.id==2.5)
R0vsRate.D.2.5 <- plot_heatmap(data=data,x.var=x.var,y.var=y.var, var.to.plot = var.to.plot, filter.coverage = filter.coverage, filter.65.delay = filter.65.delay, plot.title = plot.title, scale.x.labels=scale.x.labels,scale.y.labels=scale.y.labels,rep.0=rep.0,plot.0=plot.0)
#R0vsRate.D.2.5

```

```{r}

var.to.plot <- "Htotcum"
plot.title <- "Total Hospitalizations: Vax Rate vs. % Sero Negative Vax Comparison"

plot.title <- "R(t) = 1.9"
data <- traj.CI %>% filter(R0.id==1.9)
R0vsRate.Htotcum.1.9 <- plot_heatmap(data=data,x.var=x.var,y.var=y.var, var.to.plot = var.to.plot, filter.coverage = filter.coverage, filter.65.delay = filter.65.delay, plot.title = plot.title, scale.x.labels=scale.x.labels,scale.y.labels=scale.y.labels,rep.0=rep.0,plot.0=plot.0)
#R0vsRate.D.1.9

plot.title <- "R(t) = 1.5"
data <- traj.CI %>% filter(R0.id==1.5)
R0vsRate.Htotcum.1.5 <- plot_heatmap(data=data,x.var=x.var,y.var=y.var, var.to.plot = var.to.plot, filter.coverage = filter.coverage, filter.65.delay = filter.65.delay, plot.title = plot.title, scale.x.labels=scale.x.labels,scale.y.labels=scale.y.labels,rep.0=rep.0,plot.0=plot.0)
#R0vsRate.D.1.5

plot.title <- "R(t) = 2.5"
data <- traj.CI %>% filter(R0.id==2.5)
R0vsRate.Htotcum.2.5 <- plot_heatmap(data=data,x.var=x.var,y.var=y.var, var.to.plot = var.to.plot, filter.coverage = filter.coverage, filter.65.delay = filter.65.delay, plot.title = plot.title, scale.x.labels=scale.x.labels,scale.y.labels=scale.y.labels,rep.0=rep.0,plot.0=plot.0)

```


<!---
Differences
--->

```{r}

var.to.plot <- "D"
#y.var <- "R0.id"
y.var <- "sero.id"
x.var <- "vx.id"
scale.x.labels=NULL
scale.y.labels <- c(0, 0.5, 1)
rep.0 = NULL
plot.0 = TRUE

plot.title <- "Total Deaths: Vax Rate vs. % Sero Negative Vax Comparison"
filter.coverage <- 0
filter.65.delay <- 0

plot.title <- "R(t) = 1.9"
data <- traj.CI.diff %>% filter(R0.id==1.9)
DIFF.R0vsRate.D.1.9 <- plot_heatmap(data=data,x.var=x.var,y.var=y.var, var.to.plot = var.to.plot, filter.coverage = filter.coverage, filter.65.delay = filter.65.delay, plot.title = plot.title, scale.x.labels=scale.x.labels,scale.y.labels=scale.y.labels,rep.0=rep.0,plot.0=plot.0)
#R0vsRate.D.1.9

plot.title <- "R(t) = 1.5"
data <- traj.CI.diff %>% filter(R0.id==1.5)
DIFF.R0vsRate.D.1.5 <- plot_heatmap(data=data,x.var=x.var,y.var=y.var, var.to.plot = var.to.plot, filter.coverage = filter.coverage, filter.65.delay = filter.65.delay, plot.title = plot.title, scale.x.labels=scale.x.labels,scale.y.labels=scale.y.labels,rep.0=rep.0,plot.0=plot.0)
#R0vsRate.D.1.5

plot.title <- "R(t) = 2.5"
data <- traj.CI.diff %>% filter(R0.id==2.5)
DIFF.R0vsRate.D.2.5 <- plot_heatmap(data=data,x.var=x.var,y.var=y.var, var.to.plot = var.to.plot, filter.coverage = filter.coverage, filter.65.delay = filter.65.delay, plot.title = plot.title, scale.x.labels=scale.x.labels,scale.y.labels=scale.y.labels,rep.0=rep.0,plot.0=plot.0)
#R0vsRate.D.2.5

```

```{r}

var.to.plot <- "Htotcum"

plot.title <- "R(t) = 1.9"
data <- traj.CI.diff %>% filter(R0.id==1.9)
DIFF.R0vsRate.Htotcum.1.9 <- plot_heatmap(data=data,x.var=x.var,y.var=y.var, var.to.plot = var.to.plot, filter.coverage = filter.coverage, filter.65.delay = filter.65.delay, plot.title = plot.title, scale.x.labels=scale.x.labels,scale.y.labels=scale.y.labels,rep.0=rep.0,plot.0=plot.0)
#R0vsRate.D.1.9

plot.title <- "R(t) = 1.5"
data <- traj.CI.diff %>% filter(R0.id==1.5)
DIFF.R0vsRate.Htotcum.1.5 <- plot_heatmap(data=data,x.var=x.var,y.var=y.var, var.to.plot = var.to.plot, filter.coverage = filter.coverage, filter.65.delay = filter.65.delay, plot.title = plot.title, scale.x.labels=scale.x.labels,scale.y.labels=scale.y.labels,rep.0=rep.0,plot.0=plot.0)
#R0vsRate.D.1.5

plot.title <- "R(t) = 2.5"
data <- traj.CI.diff %>% filter(R0.id==2.5)
DIFF.R0vsRate.Htotcum.2.5 <- plot_heatmap(data=data,x.var=x.var,y.var=y.var, var.to.plot = var.to.plot, filter.coverage = filter.coverage, filter.65.delay = filter.65.delay, plot.title = plot.title, scale.x.labels=scale.x.labels,scale.y.labels=scale.y.labels,rep.0=rep.0,plot.0=plot.0)

```


## Scenario output: Heatmaps {.tabset}

### Total Deaths: Vaccination rate vs. % Sero+ Vaccinated

**Differences from no vaccination**

```{r}
DIFF.R0vsRate.D.1.9 + DIFF.R0vsRate.D.1.5 + DIFF.R0vsRate.D.2.5
```

**Totals**

```{r}
R0vsRate.D.1.9 + R0vsRate.D.1.5 + R0vsRate.D.2.5
```


### Total Hospitalizations: Vaccination rate vs. % Sero+ Vaccinated

**Differences from no vaccination**

```{r}
DIFF.R0vsRate.Htotcum.1.9 + DIFF.R0vsRate.Htotcum.1.5 + DIFF.R0vsRate.Htotcum.2.5
```

**Totals**

```{r}
R0vsRate.Htotcum.1.9 + R0vsRate.Htotcum.1.5 + R0vsRate.Htotcum.2.5
```


<!---

### Peak Hospitalizations: Vaccination rate vs. % Sero+ Vaccinated

**Differences from no vaccination**

```{r}
R0vsRate.Htot.DIFF
```

**Totals**

```{r}
R0vsRate.Htot
```

--->

{-}


## Scenario output: Timeseries {.tabset}

### Faceted plot: All variables (shows scenario inputs)

```{r}
##################################################
## Plot the scenarios

#traj.CI <- rbind(scenarios.out.realistic.0, scenarios.out.realistic.ALL)

data.in <- latest_data %>% select(c("D","I_detect_new"))
endDatePlot=last.date.plot.Vx
startDatePlot.in <- "2020-10-01"
#vars.to.plot <- c("Vx.given","Itot","Htot","D","R0_t")
vars.to.plot <- c("Vx.given","Vx.given.tot","Vx.given.65","Vx.given.65.tot", "R_vx", "sero_vx", "Itot","I_detect_new", "Htot","D","R0_t","R_out")

#data.plot.grid <- traj.CI %>% filter(vx.coverage.id==0.8) %>% filter(R0.id > 0.8) %>% filter(R0.id < 2.7)
#filter.scenarios <- NULL

data.plot.grid <- traj.CI %>% filter(R0.id==1.9)
#filter.scenarios = c(1:6, 8:12, 14:18)

plot.SCENARIOS.ALL <-  plot.SCENARIOS(traj.CI=traj.CI, data.in=data.in, startDatePlot=startDatePlot.in, endDatePlot=endDatePlot, vars.to.plot = vars.to.plot, filter.scenarios=filter.scenarios)
#plot.SCENARIOS.ALL

```


```{r}
plot.SCENARIOS.ALL

```

<!---
### Single plot: Individual variable

Hospitalizations Timeseries


```{r, eval=FALSE, inclue=FALSE}
vars.to.plot <- "Htot"
y.max.in <- 14000
startDatePlot <- "2020-11-01"
chart.title <- "Hospitalizations"
plot.scenarios.single.state <- plot.together.noribbon(traj.CI=traj.CI , data.in=NULL, endDatePlot=endDatePlot, vars.to.plot=vars.to.plot, y.lab.in=vars.to.plot, y.max.in=y.max.in, chart.title=chart.title, plot.capacity=NULL, plot.annotations=NULL, startDatePlot=startDatePlot)
#plot.scenarios.single.state

```

```{r, eval=FALSE, inclue=FALSE}
plot.scenarios.single.state
```

---> 



























