---
title: "COVID19 Modeling for Los Angeles County"
subtitle: Analysis updated with data as of `r Sys.Date()`
author: "University of Southern California, Department of Preventive Medicine"
output:
  html_document:
    css: styles.css
    toc: yes
    toc_depth: 2
    toc_float: yes
editor_options:
  chunk_output_type: console
---

```{r, include=FALSE, eval=FALSE}
# NOTES TO REMEMBER
# Both Susceptible and Recovered are vaccinated
# Vaccine efficacy delay vx.delay stored in prior_param.R (takes hold immediately after vx.delay)
```



<!--Initialize-->

``` {r setup, include=FALSE}

### Install necessary packages and get started

library(reshape2)
library(tidyverse)
library(ggplot2)
library(plotly)
library(ggrepel)
library(bindata)
library(odin)
library(fitR)
library(knitr)
library(EasyABC)
library(gridExtra)
library(odin)
library(lubridate)
library(EasyABC)
library(gridExtra)
library(kableExtra)
library(plyr)
library(dplyr)
library(data.table)
library(scales)
library(EasyABC)
library(patchwork)

library(tidyr)
library(readr)
library(purrr)
library(tibble)
library(stringr)
library(forcats)
library(network)
library(tidygraph)
library(ggraph)
library(visNetwork)
library(networkD3)
library(ggmosaic)
library(formattable)
library(DT)
library(reshape)
library(here)
library(fs)
library(MASS)
library(plotly)


lang_output <- function(x, lang) {
  cat(c(sprintf("```%s", lang), x, "```"), sep = "\n")
}
r_output <- function(x) lang_output(x, "r")

knitr::opts_chunk$set(
  fig.width = 9.5,
  fig.height = 8,
  eval=TRUE,
  echo=FALSE,
  warning=FALSE,
  cache=FALSE,
  message=FALSE,
  include=TRUE
  )

code.dir=here("code/")
data.dir=here("data/")
result.dir = here("results/")
fig.dir = here("figs/")
output.dir = here("output/")
code.paper.dir=here("code/epi_model_code")
code.risk.dir=here("code/risk_model_code/")
code.scenarios.dir=here("code/scenarios_code/")
```

<!--Set global options-->

```{r options, include=FALSE}
print.output <- FALSE
days.truncate <- 0
endDatePlotGlobal <- as.Date("2020-12-31")
last.date.plot.Vx <- as.Date("2021-06-01")
```


<!--Read in epidemic model, functions, COVID data-->

```{r read-in-model-supporting-functions, include=FALSE}

###################################################################################################
## LOAD EPIDEMIC MODELS
## And compile the model
path_seihqdr_model <- path(code.paper.dir, "stochastic_SEIAHQDR_Alphat_rt.R")
seihqdr_generator <- odin::odin(path_seihqdr_model)

path_Vx_model <- path(code.paper.dir, "stochastic_SEIAHQDR_Vx.R")
Vx_generator <- odin::odin(path_Vx_model)


###################################################################################################
## LOAD DATA PROCESSING AND MODEL ESTIMATING FUNCTIONS
model_functions <- path(code.paper.dir, "data_model_fun.R")
source(model_functions)

###################################################################################################
## LOAD PLOTTING FUNCTIONS
plot_code <- path(code.paper.dir, "plotting_fun_NEW.R")
source(plot_code)

###################################################################################################
## LOAD TABLES FUNCTIONS
tables_code <- path(code.paper.dir, "tables_fun.R")
source(tables_code)

###################################################################################################
## COVID INPUT DATA
# latest_data: cumulative and daily counts for "Htotcum","D","Vcum","Idetectcum","H_new","D_new"
# no_obs: number of observation days
latest_data <- latest_covid_data(truncate=days.truncate)
no_obs <- nrow(latest_data)

```


<!--Model Fitting-->

```{r include=FALSE}

## SOURCE PRIOR PARAMETERS
## Provides output in form of a prior.par list
## Note: Beta(t), Alpha(t), Kappa(t), Delta(t) are read in from file
prior_param_input <- path(code.paper.dir, "prior_param.R")
source(prior_param_input)
# prior.par

## SUMMARY STATISTICS COMPUTED ON DATA
summarydata <- sum.stats.SIMTEST(latest_data,include.R = FALSE)
model.R <- model.1sim.stats.no.R  # From supporting_functions

### NUMBER OF OUTPUTS
# n_calibration = 10000
# n_rec = 2000

n_calibration = 1000
n_rec = 100

## FIT MODEL
ABC_out<-ABC_mcmc(method="Marjoram",model=model.R,prior=prior.par,
                       summary_stat_target=summarydata, n_calibration=n_calibration,
                       tolerance_quantile=0.1,verbose=FALSE,progress=TRUE, n_rec=n_rec)

ABC.par.out <- as.data.frame(ABC_out$param)
ABC.out.mat <- ABC_out$param
par.vec.length <- nrow(ABC_out$param)

```


<!--Simulate model-->
<!--Get compartment variables over time with CI-->
<!--Get CFR/IFR-->

```{r include=FALSE}
###################################################################################################
## GET VACCINE EFFICACY DELAY "vx.delay" from prior_param_input
prior_param_input <- path(code.paper.dir, "prior_param.R")
source(prior_param_input)

ABC.out.mat <- ABC_out$param
par.vec.length <- nrow(ABC_out$param)
iter <- 10
time.steps <- last.date.plot.Vx - as.Date("2020-03-01") + 50
vars.to.plot <- vars.plus.Vx
vx.delay <- 20
vx.coverage <- .25

## FUNCTION MODEL.OUTPUT.TO.PLOT.SIM
## Calculates mean and CI of each estimated parameter & CFR/IFR
## Uses correlated.param.SIM
## Reads in Beta, Alpha, Kappa, Delta from file
traj.0 <- model.output.to.plot.SIM(ABC.out.mat=ABC.out.mat, vx.delay=vx.delay, vx.coverage = vx.coverage, par.vec.length=par.vec.length, iter=iter, time.steps=time.steps, vars.to.plot = vars.to.plot)

```


```{r include=FALSE}

###################################################################################################
## Plot all variables current date

time.steps.4.plot = last.date.plot.Vx - as.Date("2020-03-01") +1
data.in <- latest_data
vars.to.plot <- vars.plus.Vx

plot.all.variables.curr.date <- 
plot.model.data.all(traj.CI = traj.0, data.in = data.in, init.date.data = "2020-03-01", date.offset.4plot = 0,  time.steps.4plot=time.steps.4.plot,
                    vars.to.plot=vars.plus.Vx)

if (print.output==TRUE){
  pdf(file = path(output.dir, "plot.all.variables.pdf"), width=10, height =10)
  plot.all.variables.curr.date
  dev.off()
}
plot.all.variables.curr.date

```


```{r include=FALSE}
time.steps.4plot = last.date.plot.Vx - as.Date("2020-03-01") + 1
data.in <- latest_data
plot.annotations <- TRUE
plot.capacity <- TRUE
ymax=NULL

var.to.plot <- "I"
plot.percent.OBS <- plot.percent.LAC(traj.CI=traj.0, data.in=data.in, init.date.data=as.Date("2020-03-01"), time.steps.4plot=time.steps.4plot, ymax=NULL, plot.capacity=NULL, plot.annotations=TRUE, var.to.plot=var.to.plot)

var.to.plot <- "Itot"
plot.percent.TOT <- plot.percent.LAC(traj.CI=traj.0, data.in=data.in, init.date.data=as.Date("2020-03-01"), time.steps.4plot=time.steps.4plot, ymax=NULL, plot.capacity=NULL, plot.annotations=TRUE, var.to.plot=var.to.plot)

date.selected <- Sys.Date()
var.to.plot <- "Itot"
percent.current <- get.current.percent(traj.CI=traj.0, date.selected=date.selected,var.to.plot = var.to.plot)

date.selected <- Sys.Date()+10
var.to.plot <- "Itot"
percent.in10days <- get.current.percent(traj.CI=traj.0, date.selected=date.selected,var.to.plot = var.to.plot)


```

## Percentage of LAC population currently infected

* **The percentage infected on `r Sys.Date()` is estimated at `r percent.current`.**

* **The percentage infected on `r date.selected`, *under the assumption of the infectious rate as of `r Sys.Date()`*, is estimated at `r percent.in10days`.**

### % LAC population currently infected: observed + unobserved infections

This plot shows the model-estimated total percentage (%) of the LAC population infected, accounting for both observed and unobserved cases.

```{r}
ggplotly(plot.percent.TOT)
```

## Estimated epidemic parameters {.tabset}

```{r include=FALSE}

endDatePlot <- endDatePlotGlobal
Fig3.plots <- plot.param.t(ABC_out = ABC_out, endDatePlot=endDatePlot)

if (print.output==TRUE){
  pdf(file = path(output.dir, "plot_Rt.pdf"), width=10, height =10)
  Fig3.plots[[1]]
  dev.off()
  
  pdf(file = path(output.dir, "plot_r_t.pdf"), width=10, height =10)
  Fig3.plots[[2]]
  dev.off()
  
  pdf(file = path(output.dir, "plot_AKD_t.pdf"), width=10, height =10)
  Fig3.plots[[3]]
  dev.off()
}

```

### Reproductive Number, $R(t)$

```{r}
Fig3.plots[[1]]
```

### Fraction of Observed Infections, $r(t)$

```{r}
Fig3.plots[[2]]
```

{-}


<!---
Single compartment plots
--->

```{r include=FALSE}

time.steps.4.plot = endDatePlotGlobal - as.Date("2020-03-01") + 1
data.in <- latest_data
plot.annotations <- TRUE
plot.capacity <- TRUE
ymax=NULL

## Get compartmental variable plots TOGETHER and print/save
plot.out.H.I <- plot.out.compartmental(traj.CI = traj.CI, endDatePlot = endDatePlot)

if (print.output==TRUE){
  pdf(file = path(output.dir, "curr_infect_TOGETHER.pdf"), width=10, height =10)
  plot.out.H.I[[2]]
  dev.off()
  
  pdf(file = path(output.dir, "curr_healthcare_TOGETHER.pdf"), width=10, height =10)
  plot.out.H.I[[1]]
  dev.off()
}

## Get plots for individual variables (for ggplotly)

var.to.plot <- "I_detect_new"
#ymax=60000
plot.I.new <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01",time.steps.4plot=time.steps.4plot, 
                                ymax=ymax, plot.capacity=plot.capacity, plot.annotations=plot.annotations, var.to.plot=var.to.plot)

var.to.plot <- "I"
#ymax=60000
plot.I <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01",time.steps.4plot=time.steps.4plot, 
                                ymax=ymax, plot.capacity=plot.capacity, plot.annotations=plot.annotations, var.to.plot=var.to.plot)

var.to.plot <- "Itot"
#ymax=200000
plot.Itot <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01",time.steps.4plot=time.steps.4plot, 
                                ymax=ymax, plot.capacity=plot.capacity, plot.annotations=plot.annotations, var.to.plot=var.to.plot)

var.to.plot <- "Htot"
#ymax = 3000
plot.Htot <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01",time.steps.4plot=time.steps.4plot, 
                                ymax=ymax, plot.capacity=plot.capacity, plot.annotations=plot.annotations, var.to.plot=var.to.plot)

var.to.plot <- "Q"
#ymax = 3000
plot.Q <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01",time.steps.4plot=time.steps.4plot, 
                                ymax=ymax, plot.capacity=plot.capacity, plot.annotations=plot.annotations, var.to.plot=var.to.plot)


var.to.plot <- "D_new"
#ymax = 200
plot.Dnew <- plot.model.single(traj.CI=traj.0, data.in=data.in, init.date.data="2020-03-01",time.steps.4plot=time.steps.4plot, 
                                ymax=ymax, plot.capacity=plot.capacity, plot.annotations=plot.annotations, var.to.plot=var.to.plot)
```

## Numbers infected {.tabset}

* **New = new daily incidence**
* **Current = current census in compartment** 
* **Cumulative = running total over time**
* Black dots depict COVID-19 data

### Current estimated total infections

```{r width=3}
ggplotly(plot.Itot)
```

### Current observed infections

```{r}
ggplotly(plot.I)
```

### New observed infections (with data)

```{r}
ggplotly(plot.I.new)
```

### Current observed and total infections (together)

```{r}
plot.out.H.I[[2]]
```

{-}

## Numbers of Hospitalizations, ICU admissions, Deaths {.tabset}

* **New = new daily incidence**
* **Current = current census in compartment** 
* **Cumulative = running total over time**
* Black dots depict COVID-19 data
* Dotted black line marks healthcare capacity limits

### Current in hospital

```{r}
ggplotly(plot.Htot)
```

### Current in ICU

```{r}
ggplotly(plot.Q)
```

### New deaths

```{r}
ggplotly(plot.Dnew)
```

### Current hospitalizations, ventilations, and new deaths

```{r}
plot.out.H.I[[1]]
```

### Probabilities of severe illness

- Probability of hospitalization given infection, $\alpha(t)$

- Probability of ICU admission given hospitalization, $\kappa(t)$

- Probability of death given ICU admission, $\delta(t)$

```{r}
Fig3.plots[[3]]
```

## Model fits {.tabset}

Summarizes the epidemic model fit with COVID-19 data for LAC from March 1 through `r as.Date("2020-03-01") + no_obs` for all disease states across multiple views: New cases, representing new daily incidence; the current number in a compartment at a specific date, relevant for understanding current prevalence rates and comparing with healthcare capacity limitations; and cumulative counts until a specific date. Observed data for available compartments with cases attributable to nursing home residents removed, are plotted as black dots. The figure demonstrates that good model fits are achieved in all compartments across time.

* **New = new daily incidence**
* **Current = current census in compartment** 
* **Cumulative = running total over time**
* Black dots depict COVID-19 data, with counts from outbreaks in nursing homes removed
* The dashed line represents healthcare resource capacity limits

```{r include=FALSE}

###################################################################################################
## Plot all variables current date

last.plotting.date <- last.date.plot.Vx
time.steps.4.plot = last.plotting.date - as.Date("2020-03-01") +1
data.in <- latest_data
vars.to.plot <- vars.plus.Vx

plot.all.variables.curr.date <- 
plot.model.data.all(traj.CI = traj.0, data.in = data.in, init.date.data = "2020-03-01", date.offset.4plot = 0, time.steps.4plot=time.steps.4.plot,
                    vars.to.plot=vars.plus.Vx)

if (print.output==TRUE){
  pdf(file = path(output.dir, "plot.all.variables.pdf"), width=10, height =10)
  plot.all.variables.curr.date
  dev.off()
}
plot.all.variables.curr.date

```

```{r include=FALSE}

###################################################################################################
## Plot all variables plus 15 days

time.steps.4.plot = endDatePlotGlobal - as.Date("2020-03-01") + 15
data.in <- latest_data
vars.to.plot <- vars.plus.Vx

plot.all.variables.plus.15.days <- 
plot.model.data.all(traj.CI = traj.0, data.in = data.in, init.date.data = "2020-03-01", date.offset.4plot = 0, time.steps.4plot=time.steps.4.plot,
                    vars.to.plot=vars.plus.Vx)

if (print.output==TRUE){
  pdf(file = path(output.dir, "plot.all.variables.pdf"), width=10, height =10)
  plot.all.variables.plus.15.days
  dev.off()
}
#plot.all.variables.plus.15.days
```

### Model fits through `r Sys.Date()`

```{r}
plot.all.variables.curr.date
```

### Model **projections** through `r date.selected`

Projections **under the assumption of the infectious rate as of `r Sys.Date()`** 

```{r}
plot.all.variables.plus.15.days
```


## Tables: Parameter estimates {.tabset}

```{r include=FALSE}
###################################################################################################
## GET MODEL OUTPUT: summary

startDatePlot <- as.Date("2020-03-01")
endDatePlot <- endDatePlotGlobal
all_day_1s <- seq(startDatePlot,endDatePlot,by='month')
all_day_15s <- all_day_1s+14
date.in <- sort(c(all_day_1s,all_day_15s))
tables.out <- summary.table.param.CFR.IFR(traj.CI=traj.0, ABC_out=ABC_out, date.in=date.in, use.mean.select = 1, round.by.in=4)

```

### $R0$, $r(t)$, $\mu(t)$
```{r}
formattable(tables.out[[1]])
if (print.output==TRUE) write.csv(tables.out[[1]], file = path(output.dir, "R.r.mu_table.csv"))
```

### Probabilities of severe illness

- Probability of hospitalization given infection, $\alpha(t)$

- Probability of ICU admission given hospitalization, $\kappa(t)$

- Probability of death given ICU admission, $\delta(t)$

```{r}
formattable(tables.out[[2]])
akd_table <- tables.out[[2]]
if (print.output==TRUE) write.csv(tables.out[[2]], file = path(output.dir, "AKD_t_table.csv"))
```

### CFR and IFR

```{r}
formattable(tables.out[[3]])
if (print.output==TRUE) write.csv(tables.out[[3]], file = path(output.dir, "CFR_IFR_table.csv"))
```


## Figures: CFR and IFR

```{r include=FALSE}

startDatePlot <- as.Date("2020-03-01")
endDatePlot <- endDatePlotGlobal #as.Date("2021-02-01")
all_day_1s <- seq(startDatePlot,endDatePlot,by='month')
all_day_15s <- all_day_1s+14
date.in <- sort(c(all_day_1s,all_day_15s))

CFR.IFR.plots.out <- CFR.IFR.plots(traj.CI=traj.0, date.in=date.in, endDatePlot = endDatePlot)

if (print.output==TRUE){
  pdf(file = path(output.dir, "CFR_plot.pdf"), width=10, height =10)
  CFR.IFR.plots.out[[1]]
  dev.off()
  
  pdf(file = path(output.dir, "IFR_plot.pdf"), width=10, height =10)
  CFR.IFR.plots.out[[2]]
  dev.off()
}
```

### Time-varying CFR(t)

```{r}
CFR.IFR.plots.out[[1]]
```

### Time-varying IFR(t)
```{r}
CFR.IFR.plots.out[[2]]
```


# SCENARIOS

<!---
Get Alpha Kappa Delta table
--->

```{r include=FALSE}
###################################################################################################
## GET MODEL OUTPUT: summary

startDatePlot <- as.Date("2020-03-01")
endDatePlot <- endDatePlotGlobal
all_day_1s <- seq(startDatePlot,endDatePlot,by='month')
all_day_15s <- all_day_1s+14
date.in <- sort(c(all_day_1s,all_day_15s))
tables.out <- summary.table.param.CFR.IFR(traj.CI=traj.0, ABC_out=ABC_out, date.in=date.in, use.mean.select = 1, round.by.in=4)

```

<!--- 
Read in data
--->

```{r include=FALSE}
###############################################################################################################
## Read in marginal risk probability P(H|I), P(Q|H), P(D|Q) for each risk profile q, calculated by the JAM model
## Data coming from: Guan et al. 2020, Petrilli et al. 2020
Pr.H <- read.csv(path(data.dir, "Pr.H.csv"), sep=",", header=TRUE,row.names = 1)
Pr.Q <- read.csv(path(data.dir, "Pr.Q.csv"), sep=",", header=TRUE,row.names = 1)
Pr.D <- read.csv(path(data.dir, "Pr.D.csv"), sep=",", header=TRUE,row.names = 1)

## Get profile matrix X.mat
X.mat <- as.matrix(dplyr::select(Pr.H, -1))
n_factors <- ncol(X.mat)
n_profiles <- nrow(X.mat)

#########################################################################################################
## Read in prevalence of each risk factor p in the population for LA County
## Data coming from:
#### [Los Angeles County Health Survey](http://www.publichealth.lacounty.gov/ha/hasurveyintro.htm)
#### [California Health Information Survey](http://ask.chis.ucla.edu)
Pop.prevalence <- read.csv(path(data.dir, "Pop.prevalence.LA.csv"), sep=",", header=TRUE,row.names = 1 )
Pop.prev.matrix<-as.matrix(Pop.prevalence)

#########################################################################################################
## Read in correlation structure, $\Sigma$, between the risk factors p
## Correlation structure is weighted according to the prevalence of each race/ethnicity in LA County
## Calculated using data coming from: The National Health and Nutrition Examination Survey (NHANES)
SIGMA <- read.csv(path(data.dir, "SIGMA.csv"), sep=",", header=TRUE,row.names = 1)

```

<!---
Calculate prevalence of each profile in overall LAC population
--->

```{r riskprofiles, include=FALSE, eval=TRUE}
calc_profile_prev<- path(code.risk.dir, "calc_profile_prev.R")
source(calc_profile_prev)

## OUTPUT
# profile.cnt.freq
```

<!---
Estimate risk probabilities with baseline from epidemic model
--->

```{r estimate-risk-integrated}

##################################################
## INPUTS: TIMES
### Chosen times to run analysis at

t1 <- "2020-05-15"
t2 <- "2020-12-15"
table.dates <- c("May.15", "Dec.15")
times <- c("t1","t2")
times.dates <- as.Date(c(t1,t2))
n.times <- length(times)

# t2 <- "2020-07-15"
# t3 <- "2020-09-15"
# t4 <- "2020-10-15"
# table.dates <- c("May.15","Jul.15","Sep.15","Oct.15")
# times.dates <- as.Date(c(t1,t2,t3,t4))
# times <- c("t1","t2","t3","t4")


##################################################
## INPUTS: OBSERVED LAC DATA ON ILLNESSES
### Observed LAC age prevalence in (I) infections
n.dates.LAC.obs.age <- length(times)
freq.LAC.obs.age <- matrix(nrow=3, ncol=n.dates.LAC.obs.age)
colnames(freq.LAC.obs.age) <- times
rownames(freq.LAC.obs.age) <- c("Age0.19","Age20.64","Age65.")

freq.LAC.obs.age[,1] <- c(0.035, 0.749, 0.216)  # May.15
freq.LAC.obs.age[,2] <- c(0.115, 0.783, 0.102)  # Oct.15


##################################################
## INPUTS: EPIDEMIC MODEL
## Get mean estimates of Alpha(t), Kappa(t), Delta(t) at each time point 
akd_table <- tables.out[[2]]
table1 <- akd_table
for (i in 1:2){  table1[i,] <- akd_table[i,] %>% mutate_if(is.character, function(x) unlist(strsplit(x, " "))[1])}
table1 <- as.data.frame(apply(table1, 2, as.numeric)) 
rownames(table1) <- c("t1","t2")

## Create extra rows representing Alpha, Kappa, Delta values for t > 2 (with same values for Alpha, Kappa, Delta as t2)
if (n.times > 2){ 
  for (exrow in 3:n.times) table1[exrow,] <- table1[2,] 
  rownames(table1) <- times
  }

risk.probs.POSTERIORS <- table1

##################################################
## INPUTS: PROFILE FREQUENCY
### Estimated frequency of each risk profile
freq.PREV.q <- as.vector(profile.cnt.freq[,1])

##################################################
## INPUTS: JAM ESTIMATED CONDITIONAL RISK EFFECTS
### Read in JAM produced conditional effect estimates
psi.mat = read.csv(path(data.dir, "psi.conditional.effect.estimates.csv"), sep=",", header=TRUE,row.names = 1)
rownames(psi.mat) <- colnames(X.mat)
psi.mat[1,] <- c(rep(-1,times=3))
psi.mat[4,] <- c(rep(2,times=3))

##################################################
## APPLY CODE TO GET ESTIMATE RISK PROBABILITIES WITH BASELINE FROM EPIDEMIC MODEL
calc_integrated_risk_model<- path(code.risk.dir, "integrated_risk_model.R")
source(calc_integrated_risk_model)

# Pr.freq.FUN.out <- Pr.freq.FUN(X.mat=X.mat, freq.PREV.q = freq.PREV.q, 
#                                freq.LAC.obs.age=freq.LAC.obs.age, logit.SEIR.est=logit.SEIR.est,psi.mat=psi.mat)
# ### OUTPUTS
# Pr.OUT <- Pr.freq.FUN.out[[1]]
# freq.OUT <- Pr.freq.FUN.out[[2]]   

```


<!---
Scenarios: Get Alpha, Kappa, Delta with populations protected
--->

```{r scenarios, include=FALSE}

##################################################
## SOURCE SCENARIOS FUNCTIONS
scenarios_functions <- path(code.scenarios.dir, "scenarios_fun_TEST.R")
source(scenarios_functions)

##################################################
## INPUTS for getting % removed for various scenarios

# n.days.65.vx <- 60
# vx.coverage.65 <- vx.coverage
# 
# #percent.to.remove <- c(0,0.5,1) #c(1,0.5,0) 
# percent.to.remove <- round(seq(0,vx.coverage.65, length = n.days.65.vx),3)
# n.protect.scenario <- length(percent.to.remove)
# factor.to.remove <- 4  # Age.65.

##################################################
## Name the scenarios

## Vacination overall scenarios
n.vx.scenario <- 3
vx.scenarios.mat <- matrix(NA, nrow=n.vx.scenario, ncol=6)
colnames(vx.scenarios.mat) <- c("index","name.vx", "vx_y.vals", "start.date.vx","vx.coverage","delay.start.65.vx")
vx.scenarios.mat[,"index"] <- c(1:n.vx.scenario)
vx.scenarios.mat[,"name.vx"] <- c("vx.FAST","vx.EXPECTED","vx.SLOW")
vx.scenarios.mat[,"vx_y.vals"] <- c("nvx_y_FAST","nvx_y","nvx_y_SLOW")
vx.scenarios.mat[,"start.date.vx"] <- c("2020-09-01","2020-12-16","2021-02-16") #c("2020-12-16","2021-01-15","2020-03-01")
vx.scenarios.mat[,"vx.coverage"] <- c(.8,.8,.8)
vx.scenarios.mat[,"delay.start.65.vx"] <- c("10","30","90")


vx.scenarios.mat <- rbind(vx.scenarios.mat,vx.scenarios.mat)
vx.scenarios.mat[,"index"] <- c(1:6)
vx.scenarios.mat[,"vx.coverage"] <- c(rep(.8,3),rep(.6,3))
vx.scenarios.mat[,"name.vx"] <- paste(vx.scenarios.mat[,"name.vx"], ".coverage", vx.scenarios.mat[,"vx.coverage"], sep = "")

# vx.scenarios.mat <- rbind(vx.scenarios.mat,vx.scenarios.mat)
# vx.scenarios.mat[,"index"] <- c(1:6)
# vx.scenarios.mat[,"vx.coverage"] <- c(rep(1,3),rep(.25,3))
# vx.scenarios.mat[,"name.vx"] <- paste(vx.scenarios.mat[,"name.vx"], ".coverage", vx.scenarios.mat[,"vx.coverage"], sep = "")


## Vaccination 65+ rate scenarios
# n.protect.scenario <- 3
# protect.scenarios.mat <- matrix(NA, nrow=n.protect.scenario, ncol=5)
# colnames(protect.scenarios.mat) <- c("index","protect.name","start.date.65","n.days.65.vx","vx.coverage.65")
# protect.scenarios.mat[,"index"] <- c(1:n.protect.scenario)
# protect.scenarios.mat[,"protect.name"] <- c("Alpha_t.EARLY","Alpha_t.EXP","Alpha_t.LATE")
# protect.scenarios.mat[,"start.date.65"] <- c("2020-12-16","2020-12-16","2020-12-16") #c("2020-12-16","2021-01-15","2020-03-01")
# protect.scenarios.mat[,"n.days.65.vx"] <- c(5,75,300)
# protect.scenarios.mat[,"vx.coverage.65"] <- c(1,.75,.1)

## NPI scenarios
# NPI.scenarios.mat <- matrix(NA, nrow=3, ncol=3)
# colnames(NPI.scenarios.mat) <- c("index","NPI.name","Beta_y_vals")
# NPI.scenarios.mat[,"index"] <- c(1:3)
# NPI.scenarios.mat[,"NPI.name"] <- c("NPI.Bad","NPI.Obs", "NPI.Good")  #c("NPI.Obs","NPI.Mod","NPI.None")
# NPI.scenarios.mat[,"Beta_y_vals"] <- c("Beta_y_HIGH", "Beta_y", "Beta_y_LOW" )  #c("Beta_y","Beta_y_moderate","Beta_y_nothing")
# NPI.scenarios.mat <- as.data.frame(NPI.scenarios.mat)
# NPI.scenarios.mat

mu.scenario.in <- seq(0.1,.9,by=.1) #seq(0.1,.6,by=.25)

##################################################
## Run the scenarios
start_time = 45
num.to.run = 50
ABC.out.mat.scenarios = ABC.out.mat[c(1:num.to.run),]
iter=10
time.steps <- last.date.plot.Vx - as.Date("2020-03-01") + 50
vx.delay <- 20

correlated.param.SCENARIOS.out <- correlated.param.SCENARIOS( ABC.out.mat=ABC.out.mat.scenarios, iter=iter, time.steps=time.steps, 
                                                  vx.scenarios.mat=vx.scenarios.mat, 
                                                  mu.scenario.in=mu.scenario.in, 
                                                  X.mat=X.mat, freq.PREV.q=freq.PREV.q, freq.LAC.obs.age=freq.LAC.obs.age,
                                                  logit.SEIR.est=logit.SEIR.est, psi.mat=psi.mat, vx.delay=vx.delay)

traj.CI <- correlated.param.SCENARIOS.out
# traj.CI.1 <- correlated.param.SCENARIOS.out
# traj.CI.05 <- correlated.param.SCENARIOS.out 
# traj.CI.025 <- correlated.param.SCENARIOS.out 
# 
# traj.CI <- rbind(traj.CI.1, traj.CI.05, traj.CI.025)

##################################################
## Plot the scenarios

data.in <- latest_data %>% select(c("D","I_detect_new"))
endDatePlot=last.date.plot.Vx
startDatePlot.in <- "2020-10-01"
vars.to.plot <- c("Vx.given","Itot","Htot","D","R0_t")
#vars.to.plot <- c("Vx.given","Vx.given.tot","Vx.given.65","Vx.given.65.tot", "Itot","I_detect_new", "Htot","D","R0_t","CFRactual")

traj.CI <- correlated.param.SCENARIOS.out
filter.scenarios <- NULL

plot.SCENARIOS.ALL <-  plot.SCENARIOS(traj.CI=traj.CI, data.in=data.in, startDatePlot=startDatePlot.in, endDatePlot=endDatePlot, vars.to.plot = vars.to.plot, filter.scenarios=filter.scenarios)
plot.SCENARIOS.ALL

# filter.scenarios=c(4:9)
# plot.SCENARIOS.filter <-  plot.SCENARIOS(traj.CI=traj.CI, data.in=data.in, endDatePlot=endDatePlot, vars.to.plot = vars.to.plot, filter.scenarios=filter.scenarios)
# 
# if (print.output==TRUE){
#   pdf(file = path(output.dir, "plot.scenarios.OUT.ALL.pdf"), width=10, height =10)
#   plot.SCENARIOS.ALL
#   dev.off()
#   
#   pdf(file = path(output.dir, "plot.scenarios.OUT.filter.pdf"), width=10, height =10)
#   plot.SCENARIOS.filter
#   dev.off()
# }

```


```{r eval=FALSE, include=FALSE}
##################################################
## Plot the scenario policies to run

# plot.scenarios.in <- plot.SCENARIOS.input(ABC_out=ABC_out, 
#                                           NPI.scenarios.mat=NPI.scenarios.mat,
#                                           protect.scenarios.mat=protect.scenarios.mat, 
#                                           weighted.avg.scenarios=weighted.avg.scenarios.overall, 
#                                           endDatePlot=endDatePlot)
# if (print.output==TRUE){
#   pdf(file = path(output.dir, "plot.scenarios.IN.NPI.pdf"), width=10, height =10)
#   plot.scenarios.in[[1]]
#   dev.off()
#   
#   pdf(file = path(output.dir, "plot.scenarios.IN.Protect.pdf"), width=10, height =10)
#   plot.scenarios.in[[2]]
#   dev.off()
# }

```

